\thetitle

### 2021-02-22 writing/landscape.tex
organize sections/titles/labels in paper
overfull box

\section{How to Think About All Three Systems} 
\label{sec:landscape}

@@

When run, the program may fail with an exception if \texttt{client} tries to
inspect the elements of the list that \texttt{typed-pack} and
\texttt{crypto-pack} are supposed to produce. The information in this exception,
plus its stack trace, or may not help the programmer find the source of the
impedance mismatch between the specified return types of {\tt pack} in the two
typed modules and the actual return value of {\tt pack}.

>>>>

@@

When run, the program may raise an exception if \texttt{client} tries to
inspect the elements of the list that \texttt{typed-pack} and
\texttt{crypto-pack} are supposed to produce. The information in this exception,
plus its stack trace, or may not help the programmer find the source of the
impedance mismatch between the specified return types of {\tt pack} in the two
typed modules and the actual return value of {\tt pack}.
